---
title: "micro612.1_assignment"
author: "Sarah S. Bassiouni"
date: "March 18, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
><i>Directions:
Your assignment is to create an html document where you analyze the gap minder data to answer a specific question you had about the data. The document should include a paragraph with R code embedded in the paragraph and the document should also include a figure that fits with the question you were interested in. You should upload the Rmd, html, and any other files to your github account. When it is complete, please send me an email with a link to your repository. This will be due March 18th.</i>

## Assignment for Micrbiol 612.1, Winter 2016

For this assignment, I wanted to answer the specific question, "using the gapminder dataset, how has life expectancy changed over time, from 1952 to 2007, in each of the continents?"

To do so, I plotted life expectancy over time for each continent on the same graph.  Continents were uniquely colored to visually distinguish. Using geom_smooth, I plotted a regression line for each continent; this essentially resulted in a summary of the life expectancy for that continent.

```{r, echo=FALSE}
plot(pressure)
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
